% Discussion v2 (post v2 round-2 honest non-rejection framing).

\paragraph{Headline.}
On the unified ESMO+ASCO+NCCN HR+/HER2- mBC decision tree (25 nodes) against a 65-edge trial-DAG drawn from a systematically-searched 81-trial corpus, the strict-tolerance evidence-free decision-point ratio was 0.40 (Clopper-Pearson 95\% CI 0.21--0.61). The pre-registered one-sided exact binomial test of $H_0: \mathrm{EFDPR} \le 0.25$ marginally failed to reject at $\alpha = 0.05$ with $P = 0.071$. ESCAT-aligned and liberal tolerance gave identical estimates ($P = 0.071$). The pilot-to-production scaling from 16 nodes (v1.0.0 pilot, $\hat p = 0.31, P = 0.37$) to 25 nodes (v2.0.0 production, $\hat p = 0.40, P = 0.071$) produced a directional shift consistent with substantial composition-across-non-overlapping-trials, but did not achieve confirmatory rejection at single-tumour scale.

\paragraph{What the framework actually measures.}
The strict concordance algorithm is a deliberately conservative model: it counts as evidence-free any guideline node where no single pivotal trial enrolled exactly the (state, biomarker) population the guideline assumes. This is by design. The point is to make explicit, on one diagram, where the guideline tree is supported by direct trial chains versus where it is supported by composition across non-overlapping trials. Composition-across-non-overlap is a routine and often unavoidable practice for rapidly evolving fields; it is not illegitimate, but it has not been counted before.

\paragraph{Where the gap is largest.}
Three structural patterns dominate the 10 evidence-free nodes under strict concordance: (i) post-CDK4/6i settings where the canonical supporting trial enrolled a post-AI rather than post-CDK4/6i population (G9 no-actionable, G13 post-CDK4/6i+post-endo everolimus salvage --- both inherited from BOLERO-2's pre-CDK4/6i-era enrolment); (ii) NCCN-specific TROP2-ADC and datopotamab deruxtecan nodes (G21); and (iii) ASCO-specific special-population nodes (G17 visceral-crisis, G22/G24 indolent-disease single-agent endocrine, G25 post-everolimus salvage). After adding BYLieve (post-CDK4/6i PIK3CAmut, NCT03056755) and the corrected SERENA-6 (NCT04964934) to the corpus, the post-CDK4/6i PIK3CAmut (G7) and post-endo ESR1mut early-switch (G19) nodes are now supported under strict tolerance.

\paragraph{Operationalization discordance.}
On 81 trials and 3,160 trial pairs the prior-CDK4/6i inclusion variable had ODI 0.64 (bootstrap 95\% CI 0.62--0.66) --- the most consequential single-variable heterogeneity. Trials variously require, exclude, or permit prior CDK4/6i, and post-CDK4/6i subgroups derived from permit-prior-CDK4/6i populations cannot be cleanly combined with post-CDK4/6i subgroups from require-prior-CDK4/6i populations. ESR1 mutation definitions (ODI 0.38) showed the second-largest discordance, driven by tissue vs plasma sampling and the variant call set. These operational findings affect not only this framework's concordance algorithm but also any network-meta-analysis that attempts to pool across post-CDK4/6i trials.

\paragraph{Three caveats.}
First, the unit of inference is the guideline decision node, not the trial. With $n = 25$ nodes the test is moderately powered ($\sim 42\%$ at $p_1 = 0.40$, $\sim 79\%$ at $p_1 = 0.50$). The pre-registered exact-binomial test did not reject ($P = 0.071$) although the point estimate (0.40) is well above the threshold (0.25). A fully-powered confirmatory study would require pooling decision nodes across multiple solid tumours; the present manuscript supplies the framework and the mBC test, but confirmatory inference at single-tumour scale remains beyond the corpus reach. Second, the LLM-extraction pipeline achieved high inter-rater agreement post-adjudication (mean PABAK 0.99) but the pre-registered Cohen's $\kappa \ge 0.70$ gate failed pre-adjudication on \texttt{post\_endo} ($\kappa = 0.40$) and on \texttt{akt\_path} ($\kappa = 0.00$ due to the well-known kappa paradox at 95\% raw agreement with skewed marginals); we report both Cohen's $\kappa$ and PABAK and disclose the failure of the Cohen's $\kappa$ gate. The post-adjudication $\kappa$ should be read as a measure of \emph{adjudicability}, not as an independent re-rating measurement. Third, the two-round internal review surfaced two missing pivotal trials (BYLieve, SERENA-6), three extraction errors (CAPItello-291, DESTINY-Breast06, TROPION-Breast01), and two state-coding adjudications (CAPItello-291 and DESTINY-Breast06 post-CDK4/6i registrational subgroup readouts); after correction the strict-tolerance EFDPR moved from 0.60 (round-0 pre-correction) to 0.48 (round-1 post-correction) to 0.40 (round-2 post-adjudication), and the primary $P$ moved from 0.0002 to 0.011 to 0.071. The honest current value is 0.40 with $P = 0.071$, which we report as a marginal non-rejection.

\paragraph{Three positives.}
First, the framework is fully reproducible from the public ClinicalTrials.gov API and the public guideline documents. The 874-candidate $\to$ 81-trial filter pipeline is committed; the dual-annotator extraction protocol and per-trial outputs are released; the adjudication rules and post-adjudication kappas are published. Second, the framework is tumour-agnostic: the (state, biomarker) node space, the concordance algorithm, and the pre-registered binomial test transfer to any solid tumour whose guideline tree composes across non-overlapping pivotal trials; mBC is the first application. Third, the pre-registered design with two-annotator validation against an explicit protocol, plus a multi-round internal adversarial review that surfaced and corrected concrete extraction errors before release (with full disclosure of the resulting point-estimate trajectory), provides a template for LLM-extraction studies that aspire to confirmatory inference rather than descriptive cohort reporting.

\paragraph{Limitations.}
The 81-trial corpus is a snapshot at freeze date 2026-05-16 and excludes trials primarily completed after 2026. The guideline encoding fixes the ESMO 2024 update, ASCO 2022 living guideline, and NCCN 2024 update; ASCO and NCCN both update more frequently than annual and the EFDPR overlay should be refreshed at each update. Eligibility coding by LLM remains imperfect for highly inferential fields; production use should retain the dual-annotator + protocol-adjudication discipline. The framework cannot adjudicate whether a given composition-across-non-overlap is clinically acceptable; that judgement remains with the guideline committee. BOLERO-2 (NCT00863655) was excluded by the prereg-v2 amendment v2.1 start-year filter (started 2009) despite being the canonical citation for everolimus + exemestane in HR+/HER2- mBC; G9 and G13 are evidence-free partly as a consequence of this filter. Finally, the v1.0.0 16-trial pilot (preserved at tag \texttt{v1.0.0}) also gave a non-rejecting result ($P = 0.37$); the v2 production result remains non-rejecting ($P = 0.071$) but moves substantially toward the rejection boundary.

\paragraph{Outlook.}
The framework, schema, decision-tree encoding, and dual-annotator extraction protocol are released to enable extension by guideline committees, trial sponsors, and meta-research groups. A community-maintained Treatment-Sequencing Evidence Atlas, refreshed at every ESMO, ASCO, and NCCN HR+/HER2- mBC guideline release, could provide a continuously-updated EFDPR overlay across solid tumours. Immediate priorities are: (i) extension to EGFR-mutant NSCLC and ctDNA-guided mCRC, where the framework can be applied with the same pre-registered binomial test on a parallel guideline-node denominator; (ii) a multi-tumour pooled analysis where the unified ESMO+ASCO+NCCN decision-tree node count is large enough to power the pre-registered test against the v1-v2 directional signal; (iii) a fully-LLM-extracted census of HR+/HER2- mBC trials with inter-rater agreement at production scale; and (iv) an interactive web viewer that lets a clinician click any guideline decision node and see, in one screen, every trial-DAG edge that supports it and every edge that does not.
