%% Supplement — Paper A (Clinical Application, v3.0.0)
%% Target journal: JCO Precision Oncology
%% Build: latexmk -pdf supplement_paper_A.tex
\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=2.0cm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{caption}
\usepackage{microtype}
\usepackage{authblk}
\usepackage{float}
\usepackage{xcolor}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\fontsize{12}{14}\bfseries\sffamily}{\thesection}{0.6em}{}
\setlength{\parskip}{0.25\baselineskip}
\setlength{\parindent}{0pt}
\captionsetup{font=small,labelfont=bf,labelsep=period}
\renewcommand{\familydefault}{\rmdefault}

\title{\fontsize{14}{17}\bfseries\sffamily
Supplementary Material for:\\
Evidence-Free Decision Points in Biomarker-Driven Metastatic Cancer Guidelines}

\author[1,*]{Hsieh-Ting Lin}
\affil[1]{Department of Hematology \& Medical Oncology, Koo Foundation Sun Yat-Sen Cancer Center, 125 Lide Rd., Beitou Dist., Taipei 11259, Taiwan. ORCID iD: 0009-0002-3974-4528.}
\affil[*]{Correspondence: \texttt{htlin222@kfsyscc.org}.}
\date{\today}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent This document supplements the main manuscript \textit{Evidence-Free Decision Points in Biomarker-Driven Metastatic Cancer Guidelines: A Pre-Registered Multi-Tumor Audit of ESMO, ASCO, and NCCN Decision Trees in HR+/HER2- Breast Cancer and EGFR/ALK Non-Small-Cell Lung Cancer} (Paper A; tagged release \texttt{v3.0.0}; Zenodo DOI \texttt{10.5281/zenodo.20250848}).

\medskip
\noindent The four tables provided are:

\begin{itemize}
  \item \textbf{Table S1.} PRISMA-2020 reporting items modified for graph-theoretic guideline-trial concordance analysis (with graph-encoding addendum).
  \item \textbf{Table S2.} Representative per-trial structured extractions (10 of 259 pivotal trials).
  \item \textbf{Table S3.} Full 49-node ESMO/ASCO/NCCN unified decision tree with strict-tolerance concordance status.
  \item \textbf{Table S4.} Adjudication rules log consolidating the deterministic rules applied when LLM annotators disagreed.
\end{itemize}

\section*{S1: PRISMA-2020 reporting checklist (modified)}
\input{supplement_table_S1.tex}

\section*{S2: Representative per-trial structured extractions}
\input{supplement_table_S2.tex}

\section*{S3: Full 49-node guideline decision tree with concordance status}
\input{supplement_table_S3.tex}

\section*{S4: Adjudication rules log}
\input{supplement_table_S4.tex}

\end{document}
