% Supplementary material (separate PDF or appended after main text).
\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=2.0cm]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\title{\textbf{Supplementary Material} \\
A Computable Map of Treatment-Sequencing Evidence in HR+/HER2- Metastatic Breast Cancer}
\author{H.-T.\ Lin}
\date{\today}
\begin{document}
\maketitle

\section*{Supplementary Table S1. Reporting Transparency Checklist}
\noindent
This study reports a graph-theoretic computational analysis of clinical trials
and guidelines. No standard reporting guideline (TRIPOD, STROBE, PRISMA, CONSORT,
STARD) is a perfect fit. We adopt a custom transparency checklist that combines
PRISMA-2020 reporting items (relevant to evidence synthesis) with a graph-encoding
addendum specific to the present method.

\begin{longtable}{p{5.6cm}p{3.0cm}p{6.0cm}}
\toprule
\textbf{Item} & \textbf{Reported in} & \textbf{Notes} \\
\midrule
\endhead
1. Title identifies study as evidence-synthesis & Title & ``treatment-sequencing evidence'' \\
2. Structured abstract & Abstract & 300-word JCO CCI structure \\
3. Rationale & Introduction & Composition across non-overlapping trials \\
4. Objectives & Introduction & EFDPR + ODI \\
5. Eligibility criteria for trials & Methods 2.1, 2.2 & 16-trial pilot drawn from ESMO/ASCO reference lists \\
6. Information sources & Methods 2.1 & ClinicalTrials.gov v2 + ESMO 2024 \\
7. Search strategy & Methods 2.1 & Per-NCT fetch list (Supplementary Table S2) \\
8. Selection process & Methods 2.2 & Hand-curated against canonical primary publications \\
9. Data extraction process & Methods 2.2 & Schema v1.0 (frozen) \\
10. Data items & Methods 2.2 & Schema fields per Table S2 \\
11. Risk-of-bias assessment & Discussion & Reviewer-cycle-disclosed corpus-selection bias \\
12. Effect measures & Methods 2.5 & EFDPR; ODI \\
13. Synthesis methods & Methods 2.5 & Concordance algorithm \\
14. Reporting bias assessment & Limitations & Pilot-scale only \\
15. Certainty assessment & Discussion & Pre-registered tolerance levels \\
16. Study selection results & Results 3.1 & 16/16 trials retrieved \\
17. Study characteristics & Table S2 & Hand-curated schema fills \\
18. Risk of bias & Limitations & Disclosed \\
19. Results of individual studies & DAG edges & Trial primary endpoint per edge \\
20. Results of syntheses & Results 3.2--3.5 & EFDPR, ODI, sensitivity \\
21. Reporting biases & Discussion & Reviewer-cycle history \\
22. Certainty of evidence & Discussion & Pre-registered exact test failed to reject \\
23. Discussion & Discussion & Three caveats + three positives + outlook \\
24. Limitations & Discussion & Pilot scale, hand-curation, single guideline \\
25. Implications & Discussion & Outlook \\
26. Registration and protocol & Methods 2.6, prereg & \texttt{docs/prereg.md} \\
27. Support & Funding statement & No specific funding \\
28. Competing interests & Conflicts statement & None declared \\
29. Availability of data, code, materials & Statements & MIT licence, GitHub URL, Zenodo DOI at release \\
\midrule
G1. Graph node space & Methods 2.3 & (prior-state, biomarker) tuples \\
G2. Graph edge construction & Methods 2.3 & Trial $\to$ edge from required-state node to post-trial-state node \\
G3. Guideline-tree encoding & Methods 2.4 & 16-node encoding in Supplementary Table S3 \\
G4. Concordance algorithm & Methods 2.5 & State-superset + biomarker tolerance + drug match + temporal precedence \\
G5. Tolerance levels & Methods 2.5 & Strict / ESCAT / liberal, all pre-registered \\
G6. Reproducibility (seed + commit hash) & Methods 2.7 & Seed 20260516; \texttt{v1.0.0} commit \\
\bottomrule
\end{longtable}

\section*{Supplementary Table S2. Structured Trial Extractions}

The hand-curated schema v1.0 mapping for each of the 16 pivotal trials is
released as the machine-readable file \texttt{data/processed/trials\_structured.json}
in the repository. Each record contains the fields listed in Methods 2.2,
the source primary publication, and the canonical ClinicalTrials.gov NCT
identifier. The Round 1 internal review identified two NCT-misidentification
errors in the original draft (NCT03997123 was incorrectly labelled as
postMONARCH; NCT04032080 was incorrectly labelled as INAVO120); these were
corrected to NCT05169567 (postMONARCH) and NCT04191499 (INAVO120), with TROPiCS-02
(NCT03901339) and OlympiAD (NCT02000622) added to the corpus.

\section*{Supplementary Table S3. ESMO HR+/HER2- mBC Decision-Tree Encoding}

The hand-curated 16-node encoding of the ESMO 2024 update HR+/HER2- subset
is released as \texttt{data/processed/esmo\_decision\_tree.json}. Each node
records: node identifier, patient sub-state, biomarker profile, recommended
drug classes with strength-of-recommendation grade, cited pivotal trials, and
year of decision-tree introduction.

\section*{Supplementary Table S4. ODI Biomarker-Token Vocabulary}

The operational-token vocabulary used to compute the operationalization
discordance index is released as \texttt{analysis/06\_compute\_odi.py}. Each
biomarker variable (HER2-low, ESR1mut, PIK3CAmut, AKT-pathway, prior-CDK4/6i)
maps to a per-trial set of operational tokens drawn from the canonical primary
publication.

\section*{Supplementary Text 1. Pre-registration deviations}

The following pre-registration deviations are reported in the spirit of the
pre-registration commitment in \texttt{docs/prereg.md}:

\begin{itemize}
\item \textbf{Corpus expansion from prototype (6 trials) to pilot (16 trials).}
  The pilot expansion was anticipated in the prereg and is not a deviation.
  Trial selection was based on the ESMO/ASCO mBC guideline reference lists;
  a systematic ClinicalTrials.gov search is deferred to the production extension.
\item \textbf{Six NCT-identification corrections across Round 1 and Round 2 of
  internal review.} Round 1 corrected NCT03997123 (CAPItello-290 TNBC,
  misnamed postMONARCH) to NCT05169567 (real postMONARCH), and NCT04032080
  (LY3023414+prexasertib TNBC, misnamed INAVO120) to NCT04191499 (real
  INAVO120). Round 2 corrected NCT02513394 (PALLAS adjuvant, misnamed PALOMA-2)
  to NCT01740427 (real PALOMA-2); NCT02675231 (monarcHER HR+/HER2+, misnamed
  MONARCH-3) was removed as out-of-scope and MONARCH-3 was instead encoded
  at NCT02246621 (whose previous label, MONALEESA-3, was itself wrong);
  MONALEESA-3 was added at NCT02422615 (real MONALEESA-3); and NCT02763566
  (MONARCH plus postmenopausal, misnamed MONALEESA-7) was replaced with
  NCT02278120 (real MONALEESA-7). All NCT identifications in the present
  draft were verified against the ClinicalTrials.gov \texttt{briefTitle} and
  \texttt{conditionsModule} fields at the freeze date 2026-05-16. The full
  correction history is in the repository commit log.
\item \textbf{TROPiCS-02 (NCT03901339) and OlympiAD (NCT02000622) added.}
  Two trials were added during the correction passes to populate
  decision nodes that the prereg's narrative implied but the prototype
  did not include: G14 (post-CDK4/6i+post-chemo sacituzumab) and G16
  (gBRCAm PARPi). EMBRACA (talazoparib, NCT01945775), the parallel
  registrational trial for the gBRCAm node, is acknowledged in the
  guideline encoding but not included in this pilot corpus; it is queued
  for the production extension.
\item \textbf{Scope deviation: G16 (gBRCAm) is line-agnostic and not strictly
  HR+/HER2-.} OlympiAD enrolled gBRCAm metastatic breast cancer regardless
  of HR or HER2 status, so G16 sits outside the prereg's strict HR+/HER2-
  inclusion. The primary analysis includes G16 with the line-agnostic state
  token \texttt{metastatic} handled as a wildcard; a 15-node sensitivity
  analysis (Results 3.5) confirms that the EFDPR finding is robust to G16
  removal.
\item \textbf{Secondary outcomes S2, S3 reported descriptively.} The prereg
  commits to a Benjamini-Hochberg correction at $q = 0.05$ across S1, S2, S3.
  In the present pilot S1 (ODI) is reported as a per-biomarker mean Jaccard
  distance with bootstrap CI; S2 (temporal lag) and S3 (subgroup coverage)
  are reported descriptively because the small corpus precludes a meaningful
  formal test.
\item \textbf{Primary CI: Clopper-Pearson alongside bootstrap.} The prereg
  specified a 1,000-iteration bootstrap CI. We additionally report the
  Clopper-Pearson exact CI, which is the recommended primary CI in this
  small-$n$ regime; both CIs are reported in Table 2.
\item \textbf{Pre-registered exact-binomial test added as the formal primary
  test.} The prereg specified a one-sided exact-binomial test of $H_0:
  \mathrm{EFDPR} \le 0.25$; an earlier internal draft incorrectly substituted
  a CI-overlap rule. The current draft reports the exact-binomial test as the
  primary test, and the CI-overlap rule has been removed.
\item \textbf{Drug-class equivalence is an explicit table, not a prefix rule.}
  An earlier internal draft used a prefix-match rule for drug classes that was
  flagged as over-permissive in internal review; the current draft uses the
  explicit equivalence table in \texttt{analysis/05\_compute\_efdpr.py}.
\item \textbf{NCCN sensitivity analysis deferred.} The prereg flagged NCCN
  as a sensitivity-analysis source; this was deferred to the production
  extension and is disclosed here.
\item \textbf{Selection bias from guideline-list seeding.} The 16-trial pilot
  was seeded from the ESMO and ASCO guideline reference lists, which biases
  inclusion toward trials the guidelines already cite. The production extension
  will replace this seed with a systematic ClinicalTrials.gov query covering
  every phase 2/3 HR+/HER2- mBC trial registered between 2015 and 2026.
\item \textbf{G6 state recoding between Round 3 and Round 4 of internal review.}
  The Round 1 and Round 2 drafts coded G6 (AKT-pathway recommendation) at
  \texttt{state="post-CDK46i"}; the Round 3 clinical-review pass flagged this
  as over-narrow relative to ESMO 2024's actual placement of capivasertib at
  the post-endocrine line with prior CDK4/6i permitted but not required, and
  the current draft codes G6 at \texttt{state="post-endo"}. Effect on numbers:
  strict EFDPR unchanged at 0.31 (G6 stays evidence-free under strict because
  CAPItello-291's AKT-pathway enters as a subgroup readout, not a biomarker
  inclusion criterion); liberal EFDPR fell from 0.25 to 0.19 because G6 is
  now liberal-supported by CAPItello-291's subgroup readout. The 15-node
  sensitivity tracked the change: liberal 0.27 $\to$ 0.20.
\end{itemize}

\end{document}
